\documentclass{beamer}
\usepackage{beamerthemeshadow}
\begin{document}
\title{MCMC Span Experiment Report}
\author{LI Tao}

\begin{frame}
\titlepage
\end{frame}

\section{Introduction}
\begin{frame}\frametitle{Introductin}
\begin{itemize}
\item Problem: Mining frequent pattern in large-scale database efficiently.
\item Basic Idea: Use MCMC randomly traverse the data, and retrieve proper
sequence fulfil the requirement.
\end{itemize}
\end{frame}

\section{Algorithm Overview}
\begin{frame}\frametitle{Algorithm Overview}
\begin{enumerate}
\item Starts from null state as the current state 
\item If current state is max pattern, store it to the dictionary, and revert
the current state to null.
\item Calculate all the next state of the current state.
\item Check the frequency of each next state, erase those lower than
min-support.
\item Randomly pick one next state as the current state.
\item Repeat steps 2 to 5 until the size of dictionary is 20.
\end{enumerate}
\end{frame}

\section{Experiment Detail}
\begin{frame}\frametitle{Experiment Detail}
\begin{itemize}
\item Experiment Data:
\begin{itemize}
\item Trajectory of handwriting (normalized and discretized),
\item The character of the handwriting as labels, \textbf{8} labels are selected. 
\item Data Size:1236
\end{itemize}
\item Experiment:
\begin{itemize}
\item Configuration: min-support of the frequent pattern: 100
\item Accuracy of svm-prediction: 64.5833\%
\end{itemize}
\item Comparison: In the same configuration, prefixspan got 59.25\% accuracy.
\end{itemize}
\end{frame}
\end{document}
